---
  output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "75%"
)
```

# BASIC interpreter

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

This package allows you to edit and run scripts written in Dartmouth BASIC (1964). The package contains the grammar of the language, a lexer, a parser, and an interpreter. It is a port of the Python implementation by David Beasley to R and uses the R package rly. 

## Installation

You can install the current version of `basic` from Github by
entering the following commands into R:

```{r,eval=FALSE}
if (!require(devtools)) install.packages("devtools")
devtools::install_github("paulemms/basic")
```

## Usage

It is easiest to use R from the terminal in RStudio because autocompletion of R commands
soon gets annoying. In the terminal type `R` and then

```{r, message=FALSE, warning=FALSE, echo=TRUE}
library(basic)
packageVersion("basic")
```

To start the interpreter type at the R prompt:
```{r, message=FALSE, warning=FALSE, echo=TRUE, eval=FALSE}
basic_shell()
```
 

Paste the following text into the BASIC prompt:
```
10 FOR I = 1 TO 10
20 PRINT I
30 NEXT I
40 END
```

To see the listing type `LIST` and to run the script type `RUN`. Use ESC or Ctrl-C to exit
the BASIC interpreter.

The following BASIC scripts are contained within the package:
```{r, message=FALSE, warning=FALSE, echo=TRUE}
scripts_dir <- system.file('scripts', package = 'basic')
dir(scripts_dir)
```

To list and run one of these scripts type at the R prompt:
```{r, message=FALSE, warning=FALSE, echo=TRUE}
b <- basic(file = 'hello.bas', home_dir = scripts_dir)
b$list()
b$run()
```
